Browsing the Web of Factual Claims

### 2008-09-19 papers/web_of_ideas/web_of_ideas.tex
Made changes suggested by Tye

Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}. Like Think Link, wikis allow users to find information organised by topic rather than author and allow users to collaborate together to bring together all the best information about a topic. Wikipedia's greatest strength is arguable also it's greatest weakness. Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}. Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2}, but it is difficult to remove the problem entirely. While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious. Think Link tries to avoid this problem by linking claims back to the original sources that made these claims. Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim. Another key difference is that Think Link pulls allows users to provide links from the external web into its graph of claims, thus allowing readers to evaluate the truth of claims they read on arbitrary web pages rather than having to restrict their browsing to a single wiki site.

@@

Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages. Many web clipping tools are also web annotation systems.

In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them. As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''. Several more recent systems have allowed user to add links to existing pages. ENQUIRE~\cite{enquire} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it. Everything2~\cite{everything2} links each page to the most popular pages that users viewed at the same time. Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making.

One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed. This is a goal that is shared with several other projects. Kolak and Schilit~\cite{quotations,quotationsdl} finds places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted. Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus. ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you. ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger. Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.

@@

Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}). As a user browses the web, Think Link highlightes snippets of text that have been identified as making factual claims. If a user clicks on a highlighted snippet then Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}). Our intention is that Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.

Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}). This graph is managed like a Wiki, allowing any user to add new claims or snippets. As a user browses the web, they can identify snippets that make claims that are interesting or contraversion and link them into the global claim graph. Think Link is implemented as a FireFox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.

@@

When a user browses a web page, we want to make them aware of claims being made on the page that they might find interesting, or that other sources disagree with. Think Link draws attention to the factual claims that other users have identified on a web page by highlighting them (Figure~\ref{highlight}). Snippets are highlighted in red if they are contentious (other sources disagree with the claim). The highlight colors are chosen such as to be pale enough to not impede reading, but dark enough to be noticeable. A user can see what claim a snippet is making by hovering their mouse over the snippet (Figure~\ref{highlight}).

@@

If a user thinks a claim is interesting and wants to know what other sources say about it then they can open up a ``claim browser'' window (Figures~\ref{claimview} and \ref{claimbrowse_diagram}) by clicking on the highlighted snippet. The claim browser allows the user to easily view claims that support or oppose the selected claim, and the snippets of text on the web that make these claims (Figure~\ref{claimview}). 
For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the snippet that made this claim would be highlighted in red, indicating that there are web pages elsewhere that make opposing claims. If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear. This window would show that the claim ``Global Warming does not exist'' is opposed by the claim ``There is strong evidence for global warming''. If the user navigated to this new claim then they could quickly see the best claims that support the existence of global warming, and would be able to see summaries of the best sources that supported these claims.

@@

\begin{wrapfigure}{r}[0.5cm]{2cm}
\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
\end{wrapfigure}
If the current page contains snippets then a tab appears in the top left corner of the window. The tab contains a lightbulb whose color changes according to the nature of the snippets on the page - red if a snippet contains a contentious claim. This allows a user to quickly tell if a page contains something of interest without having to scroll down. Clicking on the tab opens the margin. The margin provides a summary of all the intersting claims that users have identified on the current page and is designed to mimick the traditional margin notes that readers often write on physical documents~\cite{marginalia}. To emphasise the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.

We found that when a participant sees a highlighted snippet, they will typically want to do one of four things: ignore it, remember it, delete it, or investigate it. If the user finds the snippet interesting and wants to use it later then they can bookmark it by clicking the bookmark icon that pops up when they mouse over the margin note. This will cause it to be displayed prominently in the claim browser. If the user believes the snippet to not be making the claim that it says it does or otherwise badly marked up then they can delete the snippet by clicking on the trash can icon on the margin note. If the user thinks the claim is interesting and wants to see how it relates to claims made by other snippets on the web then they can click on the highlighted text or the margin note to open the claim browser.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{../screenshots/bookmark_icons.png}
	\caption{Icons used for Claims, Snippets, and Topics}
	\label{bookmark_icons}
	\end{center}
\end{figure}

Think Link users interact with three kinds of object, each of which is associated with a different family of icons (Figure~\ref{bookmark_icons}):

\begin{itemize}
\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false. For example ``Global warming is man made''. A claim may support or oppose other claims. Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim. Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about. For example ``Global Warming'', or ``Computer Science''. A claim can have one or more topics that it is about, and a topic can have one or more more general topics. Topics are used both to organize, and to disambiguate claims. For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''. Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous.
\end{itemize}

Varients of these three icons are used consistently when refering to these three object types. 
Yellow versions of these icons are used to identify claims, folders, or snippets that the user has marked as interesting (by clicking on their icon).

Colors are also used to indicate the extent to which a claim is supported or opposed by other claims. Red means that a claim is opposed by other claims, and green means that a claim is supported by other claims and not opposed by any. The colors are chosen to fit with people's normal associations with colors, where red is commonly associated with danger (e.g. a traffic light) and yellow is the standard color used for highlighter pens.

\subsection{Collaborating to connect claims}

Think Link shares a lot in common with Wikis like Wikipedia~\cite{wikipedia}. The claim graph is shared between all users and editable by anyone. Any user can identify a claim made on a web page by selecting the web snippet that makes this claim and clicking the ``new snippet'' button on the browser toolbar. Similarly, any user can establish new supporting and opposing relationships between claims by using drag and drop within the claim browser. One can think of Think Link as being rather like a Wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.

Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim. If a user finds a snippet or claim interesting then they can mark it as such. When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them interesting.

It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with. Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets. While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering. A claim or snippet will only be deleted if many people vote to delete it and very few people bookmark it.

@@

\section{Interaction Techniques}
\label{interface}

Users interact with Think Link in four key ways. Think Link will draw attention to interesting claims on pages that the user browses; it allows the user to identify new factual claims on pages they browse; it allows them to browse the graph of related claims and identify the strongest evidence supporting or opposing the claims they are looking at; and it allows them to organize the claim graph by making new connections between existing claims and topics.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The Claim Browser Allows one to browse the argument graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}
\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
	\caption{Close up of a list of supporting claims}
	\label{claimbrowse_zoom}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/fullbrowser.png}
	\caption{The Enhanced claim browser adds additional controls}
	\label{enhancedbrowser}
	\end{center}
\end{figure}

Our users expressed an interest in using snippets to help them construct arguments that support a claim they agree with, to show them the arguments for and against a claim that they are unsure about, to collect evidence about a topic they are interested in, to share information with friends, and to see arguments against claims that they encountered on the web. We constructed the ``claim browser'' interface to help users do these things (Figure~\ref{fig:claimbrowser}).

When designing an interface to this structure, we were faced with two opposing constraints. We needed to be able to clearly view a large number of claims and topics in a small screen space, and we needed an interface that made it clear that the data was a graph rather than a tree. Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims. Tree-based outliners such as OmniOutliner~\cite{outliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.

\todo{This interface is actually closer to TheBrain than the text suggests}

After several iterations, we settled on an interface that is a dynamically reorganizing graph layed out like an outliner. Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it. Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line. Our users commented that they found it quite intuitive to navigate through a graph of claims and topics in this way. \studyresult{quote}.

The placement of objects above and below is intended to emphasize the conventional structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards. A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.

\todo{Have I seen an interface like this elsewhere? Did PARC have something like this?}

\todo{Is this interface a contribution in itself? Has an interface like this been presented before?}

Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states. When a new item is selected, it grows in size and moves to the center. Other items that were already on the screen move from their current locations to their new locations. Other objects appear and disapper by smoothly sliding into or out of view. We found that this animation helps users retain a sense of where they are with respect to what they were looking at previously and helps users avoid getting lost.

Users see a claim browser in three different places:
\begin{itemize}
\item {\bf The Main Organizer} shows two claim browsers, and allows users to use drag and drop to make new connections between claims in the two organizers. (Figure~\ref{fig:claimbrowser})
\item {\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page. (Figure~\ref{claimview})
\item {\bf The Claim Selection Window} shows one claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making. (Figure~\ref{snipsavecrop}) 
\end{itemize}

\subsection{Identifying new factual claims}
\label{newsnippet}

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram.png}
	\caption{Selecting the claim made by a new snippet}
	\label{snipsavecrop}
\end{figure}

If a user finds a snippet of text on a page that makes an interesting claim then they may want to enter it into Think Link. There are several reasons they may wish to do this. It may be that they find the snippet useful and may want to refer to it again in the future. It may be that they disagree with the claim, and want to alert other readers to the fact that there are opposing arguments, or it may be that they agree with the claim and want to provide easy access to evidence that backs it up.

To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button. This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.

Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making. To do this, Think Link presents the user with a ``claim selection'' window. This window contains a small version of the claim browser that the user can use to select the claim that the snippet is making. At the bottom of the window, we show the phrase ``the snippet text {\it snippet} claims that {\it claim}''. We found that this helps users understand the nature of a claim and its relationship to a snippet.

Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics. Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one. Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim. To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to. For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim.

This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}. This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected.

In earlier revisions of the interface it was very easy for users to quickly create new claim texts and awkward to find and reuse existing ones. This led users to create many claims that were essentially equivalent and reduced the utility of Think Link as a tool for connection snippets together.

\todo{Make new snippet icon throb when something is selected}

\subsection{Organizing factual claims}

Much of the value of Think Link comes from the connections between claims. It is thus important that it be easy to establish new connections between claims and topics.

Think Link uses the familiar drag and drop interface for establishing new connections. To establish a connection between two claims, one need simply drag one claim onto the other. In the full interface, one can open two browsers and drag points from one browser onto points on the other.

In our initial study, we found that many users did not realize that they could use drag and drop to create connections to existing claims. We rectify this, we added a notice at the top of the main organizer window (Figure~\ref{fig:claimbrowser}) telling users that they can use drag and drop.

We found that creating new connections between existing claims was one of the things that users found most difficult.

\todo{say more here}

\section{Discussion}

\subsection{Context of a Claim}

\subsection{How many claims to show}

\subsection{Beyond Claims}

\section{Implementation}

@@

\begin{itemize}
\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains a graph of claims, topics, and snippets and provides an API that allows this data to be queried and modified
\item {\bf A web UI}, written using Ruby on Rails~\cite{rails} that provides a visual interface to the claim graph
\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page. This script also provides the ability to create new snippets or display the rails interface to investigate a particular claim.
\item {\bf A browser extension}, implemented for Firefox~\cite{firefoxextension}, that inserts the page enhancement script into all pages the user browses to, and provides toolbar and context-menu shortcuts to the ``new snippet'' feature of the page enhancement script.
\end{itemize}

These components are largely independent. One could use the javascript script on a web page without using the firefox extension, by either manually including it on the page (e.g. to enhance your own blog) or by adding it using a proxy. Since the server API is public, one could write alternative tools that mark up web pages in different ways, or use the claim graph for different purposes.

The source code to Think Link is publicly available under the Apache license at the following URL:

{\b url removed for blind submission}

We expect to have a public deployment available by the time of publication.

We use icons from the free FamFamFam Silk~\cite{silkicons} collection.

@@

For the first study we recruited 12 paid participants. Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the internet to find information. We recruited participants using a posting to the Craigslist~\cite{craigslist} classified adverts site. In our advert, we expressed an interest in people who use the internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

@@

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlights and explore the interface while thinking aloud about what they saw. The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated our database with. Participants were shown an interface that is largely identical to that described earlier in this paper.

@@

In this section we present the findings from our two users studies. Findings from the two studies are presented together and clustered by topic.

@@

Response was generally positive, with many participants being very keen to use the tool soon. One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it becomes publically available. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Particpants in the second study said they found the tool ``very intuitive''.

\subsubsection{Browsing the Argument Graph}

>>>>

Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}. Like Think Link, wikis allow users to find information organised by topic rather than author and allow users to collaborate together to bring together all the best information about a topic. Wikipedia's greatest strength is arguably also its greatest weakness. Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}. Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2,wikicorrect3}, but it is difficult to remove the problem entirely. While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious. Think Link tries to avoid this problem by linking claims back to the original sources that made these claims. Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.

When a topic is heavily politicized, Wikipedia can be subject to edit wars in which people who hold one opinion delete opinions held by the other side~\cite{wikicorrect3}, making it difficult for the community to collaborate together to produce a document that is both comprehensive and unbiased. Think Link attempts to avoid this problem by taking an ``append-only, collaborative filtering'' approach. A user cannot remove claims that they disagree with\footnote{With special exceptions for dealing with spam and abuse}. Instead all they can do is vote against them, and connect them to claims that provide opposing evidence.

Another key difference between Think Link and a Wiki is that Think Link pulls the whole web into its graph of connected claims. A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.

@@

Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages. Many web clipping tools are also web annotation systems. These tools are designed for gathering and sharing interesting information, rather than for identifying the claims being made, or allowing users to navigate to related claims being made on other sites.

In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them. As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''. Several more recent systems have allowed user to add links to existing pages. ENQUIRE~\cite{enquire} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it. Everything2~\cite{everything2} links each page to the most popular pages that users viewed at the same time. Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.

One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed. This is a goal that is shared with several other projects. Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted. Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus. ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you. ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger. Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.

@@

Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}). As a user browses the web, Think Link highlights snippets of text that have been identified as making factual claims. If a user clicks on a highlighted snippet then Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}). Our intention is that Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.

Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}). This graph is managed like a Wiki, allowing any user to add new claims or snippets. As a user browses the web, they can identify snippets that make claims that are interesting or contraversion and link them into the global claim graph.

Think Link is implemented as a FireFox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.

@@

When a user browses a web page, we want to make them aware of claims being made on the page that they might find interesting, or that other sources disagree with. Think Link draws attention to the factual claims that other users have identified on a web page by highlighting them (Figure~\ref{highlight}). Snippets are highlighted in red if they are contentious (other sources disagree with the claim). The highlight colors are chosen to be pale enough to not impede reading, dark enough to be noticeable\footnote{Unless the background is close to a highlight color. Think Link does not yet adapt to different page background colors}, and different enough to be distinguishable by colorblind people.
A user can see what claim a snippet is making by hovering their mouse over the snippet (Figure~\ref{highlight}).

@@

If a user thinks a claim is interesting and wants to know what other sources say about it then they can open up a ``claim browser'' window (Figures~\ref{claimview} and \ref{claimbrowse_diagram}) by clicking on the highlighted snippet. The claim browser allows the user to easily view claims that support or oppose the selected claim, and find snippets of text on the web that make these claims (Figure~\ref{claimview}). 
For example, if a user browsed a web page that claimed ``Global Warming does not exist'', then the snippet that made this claim would be highlighted in red, indicating that there are web pages elsewhere that make opposing claims. If the user were to click on the highlighted snippet then an ``investigate claim'' window would appear (Figure~\ref{claimview}). This window would show the user that the claim ``Global Warming does not exist'' is opposed by the claim ``There is strong evidence for global warming''. If the user navigated to this new claim then they could quickly see the best claims that support the existence of global warming, and would be able to see summaries of the best sources that supported these claims.

@@

\begin{wrapfigure}{r}[0.3cm]{2cm}
\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
\end{wrapfigure}
If the current page contains snippets then a tab appears in the top left corner of the window. The tab contains a lightbulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim. This allows a user to quickly tell if a page contains something of interest without having to scroll through the whole page. Clicking on the tab opens the margin. The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimick the traditional margin notes that readers often write on physical documents~\cite{marginalia}. To emphasise the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{../screenshots/bookmark_icons2.png}
	\caption{Icons used for Claims, Snippets, and Topics}
	\label{bookmark_icons}
	\end{center}
\end{figure}

Think Link users interact with three kinds of object, each associated with a different family of icons (Figure~\ref{bookmark_icons}):

\begin{itemize}
\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false. For example ``Global warming is man made''. A claim may support or oppose other claims. Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim. Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about. For example ``Global Warming'', or ``Computer Science''. A claim can have one or more topics that it is about, and a topic can have one or more more general topics. Topics are used both to organize, and to disambiguate claims. For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''. Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous. A topic can itself by disambiguated by having a super-topic.
\end{itemize}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The claim browser visualizes the claim graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}
\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
	\caption{Close up of a list of supporting claims}
	\label{claimbrowse_zoom}
	\end{center}
\end{figure}

When designing an interface to this structure, we were faced with two opposing constraints. We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree. Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place. Tree-based outliners such as OmniOutliner~\cite{outliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.

After several iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner. Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it. Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.

The placement of objects above and below is intended to emphasize the conventional hierachial structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards. A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.

Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states. When a new item is selected, it grows in size and moves to the center. Other items that were already on the screen move from their current locations to their new locations. Other objects appear and disapper by smoothly sliding into or out of view.

Users see a claim browser in three different places. The {\bf organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}). {\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}). The {\bf Claim Selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).

\subsection{Creating new Snippets}
\label{newsnippet}

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/snipsave_diagram_full.png}
	\caption{Selecting the claim made by a new snippet}
	\label{snipsavecrop}
\end{figure}

There are several reasons a user may wish to add a snippet to Think Link. It may be that they find the snippet useful and may want to refer to it again in the future. It may be that they disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments, it may be that they think the claim argues a point well and want to be able to use it to make an argument, or it may be that they agree with the claim and want to provide easy access to evidence elsewhere that backs it up.

To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}). This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.

Once the user has identified the text in a snippet, they need to identify the claim that the snippet is making. To do this, Think Link presents the user with a ``claim selector'' window. This window contains a small version of the claim browser that the user can use to select the claim that the snippet is making.

Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics. Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one. Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim. To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to. For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim. This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}. This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected. In practice, it is inevitable that duplicates claims and topics will sometimes be created. When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.

\subsection{Organizing the Claim Graph}

Like Wikipedia~\cite{wikipedia}, Think Link allows any user to improve the information in the claim graph. The claim graph is shared between all users and editable by anyone. Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects. One can think of Think Link as being rather like a Wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.

Think Link uses collaborative filtering~\cite{collective} to highlight the most interesting claims that support and oppose another claim, and the most interesting snippets that make a claim. If a user finds a snippet or claim interesting then they can vote in favor of it by clicking on its icon, causing it to light up (Figure~\ref{bookmark_icons}). When Think Link lists claims or snippets, it will show first those that the user marked as interesting, and order the rest according to the number of other users who marked them as interesting.

It is important to avoid political fights, where two competing sides delete claims, snippets, or connections that they disagree with. Similarly, it is important to avoid vandalism, where people abuse people with competing beliefs by adding abuse claims or snippets. While we do not have a perfect solution to this problem, our current approach is to treat deletion as a special case of collaborative filtering. If a user believes a claim, topic, snippet, or connection is junk then they can request that it be deleted by clicking on the ``delete'' button. This will hide the object for the user who request deletion and reduce the score of the object for other users. If enough people vote to delete the object then its score will eventually be low enough that it is not displayed to users unless they request to see junk objects.

Unlike a Wiki, in which users can edit and delete information produced by others, and history is used to revert abusive changes, Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects. The hope is that over time ratings should converge to a steady state and edit wars should be avoided. It would not be practical for a wiki to take this approach as their data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.

Think Link uses the familiar drag and drop interface for establishing new connections. To establish a connection between two claims, one need simply drag one claim onto the other. The claim organizer window has two claim browsers, allowing a user to points from one browser onto points on the other (Figure~\ref{fig:claimbrowser}).

@@

\subsection{Implementation}

@@

\begin{itemize}
\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains the claim graph and provides an API that allows this data to be queried and modified
\item {\bf A web UI}, written using Javascript that implements the claim browser
\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page. This script displays the web UI in an iframe to pick or investigate a claim.
\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides toolbar and context-menu shortcuts.
\end{itemize}

These components are largely independent. One could use the page enhancement script on a web page without using the Firefox extension, by either manually including it on the page (e.g. to enhance your own blog) or by adding it using a proxy. Since the server API is public, one could write alternative tools that mark up web pages in different ways, or use the claim graph for different purposes.

The source code to Think Link is publicaly available under the Apache license.

@@

For the first study we recruited 12 paid participants. Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the internet to find information. We recruited participants using a posting to the Craigslist~\cite{craigslist} classified advert site. In our advert, we expressed an interest in people who use the internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

@@

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlights and explore the interface while thinking aloud about what they saw. The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with. Participants were shown an interface that is largely identical to that described earlier in this paper.

@@

In this section we present the findings from our two user studies. Findings from the two studies are presented together and clustered by topic.

@@

Response was generally positive, with many participants being very keen to use the tool soon. One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Participants said they found the tool ``very intuitive''.
